Embedded Scalars, Preferred Readings \& Prosody: {A}n Experimental Revisit

### 2015-10-17 text/paper/revision_02/paper.tex
K2 rev edits

Although restricted traditionalism does not of itself predict local
readings to be available at all and even unrestricted traditionalism
does not predict local readings for \es-sentences, many authors who
adhere to a traditionalist position propose that local readings can be
available if the embedded scalar item is prosodically marked by
contrastive stress
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,GeurtsTielvan-Tiel2013:Embedded-Scalar}. This
is taken to be continuous with other cases where pragmatic enrichments
can take scope under logical operators if the relevant focal accent is
present (\ref{bsp:Stress}).

@@

\noindent The \emph{prosodic markedness hypothesis}, as we will call
it here, is then an addition to the traditionalist's explanatory
repertoire. Under this extra assumption, local readings are a marked
phenomenon, and not the product of the same process as run-of-the-mill
scalar implicatures. If supplemented with the prosodic markedness
hypothesis, traditionalists would therefore predict that local
readings are available for \as- and \es-sentences, but only if
prosodically marked by contrastive stress.

>>>>

Although traditionalism does not predict local readings for \es-sentences, many authors who
adhere to a traditionalist position propose that local readings can be available if the
embedded scalar item is prosodically marked
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,GeurtsTielvan-Tiel2013:Embedded-Scalar}. This
is taken to be continuous with other cases where pragmatic enrichments can take scope under
logical operators if the relevant focal accent is present (\ref{bsp:Stress}).

@@

\noindent The \emph{prosodic markedness hypothesis}, as we will call
it here, is then an addition to the traditionalist's explanatory
repertoire. Under this extra assumption, local readings are a marked
phenomenon, and not the product of the same process as run-of-the-mill
scalar implicatures. If supplemented with the prosodic markedness
hypothesis, traditionalists would therefore predict that local
readings are available for \es-sentences, but only if
prosodically marked by contrastive stress.
